Recruiting Chapter

### 2020-10-27 manuscript.Rmd
draft changes

---
title: "Recruiting Chapter"
author: "Ozan Jaquette"
bibliography: ./other/burd_recruiting_chapter.bib
output: bookdown::pdf_document2
csl: ./other/apa.csl
urlcolor: blue
header-includes:
      - \usepackage{pdflscape}
---

@@

Figure X shows the "enrollment funnel," a conceptual heurisitc used by the enrollment management industry, which describe the stages in the student recruitment process (e.g., prospects, inquiries, applicants, accepted applicants, and enrolled students). For example, “prospects” are “all the potential students you would want to attract to your institution” [@RN4322]. “Inquiries” are prospects that contact the institution, including those who respond to a solicitation and those who reach out on their own. The enrollment management industry uses the enrollment funnel to inform interventions that target specific stages of the funnel.

@@

```{r, ego-table-privu, echo = FALSE}
df <- readRDS('./assets/tables/table_ego.RDS')
knitr::kable(
  df %>% select(-ID, -Characteristics), row.names = F, 
  caption = 'ego table caption') %>% landscape(margin = NULL) %>%
  kable_styling(latex_options = 'scale_down')
```

@@

![The enrollment funnel](assets/images/enrollment_funnel.png)

@@

@@

```{r two-mode-plot, fig.align = 'center', echo = FALSE, out.width = "125%", fig.cap = "caption of 2 mode graph"}
knitr::include_graphics('assets/figures/plot_g_2mode.pdf')
#https://stackoverflow.com/questions/15625990/how-to-set-size-for-local-image-using-knitr-for-markdown
```

```{r two-mode-plot-privu, fig.align = 'center', echo = FALSE, out.width = "125%", fig.cap = "caption of 2 mode graph"}
knitr::include_graphics('assets/figures/plot_g_2mode_privu.pdf')
```

@@

>>>>

---
title: "Recruiting Chapter"
author: "Ozan Jaquette"
bibliography: ./other/burd_recruiting_chapter.bib
output: bookdown::pdf_document2
csl: ./other/apa.csl
urlcolor: blue
header-includes:
      - \usepackage{pdflscape}
      - \usepackage{geometry}
---

@@

Figure \@ref(fig:em-funnel) shows the "enrollment funnel," a conceptual heurisitc used by the enrollment management industry, which describe the stages in the student recruitment process (e.g., prospects, inquiries, applicants, accepted applicants, and enrolled students). For example, “prospects” are “all the potential students you would want to attract to your institution” [@RN4322]. “Inquiries” are prospects that contact the institution, including those who respond to a solicitation and those who reach out on their own. The enrollment management industry uses the enrollment funnel to inform interventions that target specific stages of the funnel.

@@

```{r, ego-table-privu, echo = FALSE}
df <- readRDS('./assets/tables/table_ego.RDS')
knitr::kable(
  df %>% select(-Characteristics), row.names = F, # select(-ID, -Characteristics)
  caption = 'ego table caption') %>% landscape(margin = NULL) %>%
  kable_styling(latex_options = 'scale_down')
```

@@

```{r em-funnel, echo = FALSE, fig.cap = "The enrollment funnel"}
knitr::include_graphics('assets/images/enrollment_funnel.png')
#![The enrollment funnel](assets/images/enrollment_funnel.png)
```

@@

\newgeometry{margin=0cm}

@@

```{r two-mode-plot, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption of 2 mode graph"}
knitr::include_graphics('assets/figures/plot_g_2mode.pdf')
#https://stackoverflow.com/questions/15625990/how-to-set-size-for-local-image-using-knitr-for-markdown
```

```{r two-mode-plot-privu, fig.align = 'center', echo = FALSE, out.width = "75%", fig.cap = "caption of 2 mode graph"}
knitr::include_graphics('assets/figures/plot_g_2mode_privu.pdf')
```

@@

\restoregeometry
